---
  title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
  keep_md: true
---
  
  ## Loading and preprocessing the data
  ````{r}
unzip("activity.zip")
activity <- read.csv("activity.csv")
str(activity)
activity$date <- as.Date(activity$date)
```


## What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

1. Make a histogram of the total number of steps taken each day

````{r}
aggregacti <- aggregate(steps ~ date, data = activity, FUN = sum)
barplot(aggregacti$steps, names.arg = aggregacti$date, col = "lightblue",
        xlab = "Date", ylab = "Number of Steps", 
        main="Total numbers of steps taken per day")           
```                          

2. Calculate and report the mean and median total number of steps taken per day
````{r}
mean(aggregacti$steps)
````

````{r}
median(aggregacti$steps)
````
## What is the average daily activity pattern?
1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
aggreg_step_interv <- aggregate(steps ~ interval, data = activity, FUN = mean)
plot(aggreg_step_interv, type="l", col = "darkblue")
````

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}

````

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?

